Segmentation Using Attributes

### 2010-05-11 trunk/paper.tex
changes

Our work focuses on leveraging attributes to produce accurate segmentations.
The idea is to find image regions with salient attribute distributions.  If
these regions can be combined together to for larger regions with attribute 
distributions matching some object's canonical distribution then one can
declare the combined region an accurate segmentation for that object.

\begin{figure}
\centering
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
\label{fig:trucka}
}
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
\label{fig:truckb}
}
\caption{Segmentation by maximizing attribute saliency.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image 
contains a car increases.}
\label{fig:truck}
\end{figure}

In practice, however, the testing of all combinations of regions to find 
objects is intractable.  We use two approximatory algorithms operating on
a segmentation hierarchy to determine salient regions.  Both are subtractive
algorithms, which first predict attributes on the entire region and then
proceed by observing the effects of removing different regions during
a top-down traversal of the tree.  The benefit of using these methods are
that large regions that clearly don't contribute to attribute saliency
can be pruned from the tree early in the traversal.  This approach avoids
the combinatoric complexity of a full search and, even more, prunes many
regions from the segmentation tree before they even are searched, bringing
the computational complexity, in practice, to roughly $O(n)$ where $n$ is
the number of leaves in the segmentation tree.

While we focus on segmentation of known objects, we anticipate an application
that takes more advantage of attributes: that of segmenting \emph{unknown}
objects from an image that exhibit salient but unrecognized attribute
distributions.  This type of application brings out some of the true power of
attributes, that of assigning semantic meaning to unknown, segmented objects.

@@

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}
[Note: this section was lifted straight from our extended abstract
and has not yet been updated to reflect what we actually did.]

A significant amount of recent work has been done in the area of using
attributes as high-level features for image classification and object
description \cite{farhadi09, lampert09, kumar09}.  
Another area of computer vision, that of segmentation,
has seen a resurgence of popularity as methods to incorporate top-down
information into segmentation have been shown to be highly effective
\cite{borenstein04, pantofaru, gu09, russell06, malisiewicz, leibe04, hoiem05, shotton06}.  
We propose to leverage research done in both of these areas -- attributes
and top-down/bottom-up segmentation -- to produce a combined approach.

@@

Object classification can give some top-down high-level information
for segmentation. On the other hand, segmentation can provide
image-based coherence information for classification. To deal with
the problem that the bottom-up single segmentation is not accurate,
more and more algorithms are based on multiple segmentations. Gu et
al \cite{gu09} uses the hierarchical segmentation algorithm to
generate multiple segments, and detect different parts of objects in
each segment. The final objects are voted for by the various parts.
We will initially be using the same segmentation algorithm used in
this paper, but without discarding the hierarchy.
Russell et al \cite{russell06} detect the whole object in each of
the multiple segment, by assuming that most objects get segmented
correctly at least once during the multiple segmentation. Our approach
will be far less aggressive in that we will use object classes and 
features (attributes in our case) that are known \emph{a priori}.
Pantofaru et
al \cite{pantofaru} use three different segmentation algorithms to
generate the multiple segments. After detecting objects in each
segment, they merge the intersected segments as final results. In
our method, we use common knowledge of distribution of attributes to
merge segments.
Borenstein et al \cite{borenstein04} proposed a method of combining top-down
and bottom-up information to generate a high-quality segmentation.  Their
approach to the top-down is to use exemplar image fragments and match them
to the image and then refining the top-down segmentation using their
segmentation hierarchy.  Our approach is very similar to this in spirit.
While our initial estimate of segmentation is from the bottom-up (while
theirs is from the top-down) we will use the hierarchical information
from the segmentation to boost confidences of segmentation at the lowest
level, similar to what they do.

Another interesting work is that of Gould et al \cite{gould08}.  They use
superpixels for an initial segmentation, build a CRF that includes a
relative location feature in the energy function and minimizes the CRF
for a final segmentation.  The relative location feature is determined
using prior location probability maps.  Our approach is similar to this
as well, in that we will also incorporate relative location information,
although ours will use attributes' relative locations rather than object
classes.  We will also use a CRF for the final segmentation, but will
use a min-cut solution since our labels are binary.
Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
adding a latent shape parameter to the CRF.  This seems like it would be
a useful addition to our system but make the scope too large.

@@

We use similar algorithm as \cite{farhadi09} to train the attribute models. Three different type of features are used, such as HOG, texture and color descriptors\cite{farhadi09}. Those features can capture different properties. We use kmeans to quantize all the features. The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively. All the quantized features are concatenated to form the 1384 deminsional feature.

For training, we use SVM classifier with Gaussian kernel to train model for each attribute. The precision of all the attributes on the test set is illustrated in figure?.

@@

We use the segmentation
approach of \cite{arbelaez09}.  This produces a hierarchical
segmentation by first detecting contours using the \emph{gPb} detector
\cite{maire08}.  Once the contours are detected, regions are discovered using a
watershed algorithm after which an Ultrametric Contour Map (UCM) is constructed,
which defines the region hierarchy. Some example of the hierarchy segmentation is shown in figure?

After the construction of hierarchy segmentation tree, we detect all the attributes in each node, including the intermedia node and leaf node. We use the output of SVM as the confidence (not binary), so each node can be represented by the confidence distribution of all attributes.

@@

Our objective is to detect object and segment it out. In our hierarchy segmentation tree, the problem changes to how to select those nodes belong to the desired object. We estimate the probability that a node is belong to object based on the attribute confidence distribution. For each object, we manually give the desired attribute distribution by common knowledge. We use the histogram intersection between the desired distribution and the estimated confidence distribution in each node as the similarity measure. The histogram intersection is calculated as follows:

\[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|} \]

To select the nodes, we propose two different top-down prune algorithms, additive algorithm and subtractive algorithm. We use the UCM to generate two types of region tree, shown in figure \ref{fig:tree}.
The first tree is an additive tree, where regions are subdivided into successively
smaller regions moving down in the tree.  We call it ``additive'' because the
original image can be reconstructed by adding the regions from each leaf node
together.  The figures show the nodes of the trees as containing images, but in
truth the trees contain binary masks which, when applied to the original image,
produce the shown node contents.

The second tree is ``subtractive.''  The tree has identical structure to the additive
tree and each node contains the inverse of the mask of the corresponding node
in the additive tree.

The final segmentation is obtained by pruning the region tree until a final segmentation
meeting some criterion of absolute or relative attribute saliency is found.
We have two methods for pruning the tree, each showing relative strengths and
weakness.  The first is a semi-greedy additive approach which uses the additive
tree.  The second is a greedy subtractive approach.  We now discuss each of these 
in detail.

\begin{figure*}
\centering
\subfigure[]{
\label{fig:treea}
\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
}
\subfigure[]{
\label{fig:treeb}
\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
}
\caption{The two segmentation hierarchies used by the additive \subref{fig:treea}
and subtractive \subref{fig:treeb} algorithms.  The additive hierarchy breaks the
regions into smaller and smaller regions, while the subtractive hierarchy increases
the size of the regions as smaller and smaller chunks are removed from the image.}
\label{fig:tree}
\end{figure*}

@@

This pruning algorithm is based on three observations. (1) At least one node in the segmentation tree contrains the whole object. (This is always true since the root node contains the whole image). (2) If both parent node and child node have high confidence of containing the object, the segmentation of the child node is more accurate than that of the parrent node. (3) Even if the same node has high confidence of containing the object, its segmentation can still improve. The details of the additive algorithm is shown in algorithm \ref{alg:add_prune}.

The idea of the algorithm is to find the smallest discriminative regions, either positive or negative, and combine all of them together to form the final segmentation. We use three threshold for the similarity measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent perfect segment, positive segment and negative segment, respectively. If the similarity is above $thre\_perf$, which means the segmentation is perfect, we cut all the nodes below and return this segment. If the similarity is below $thre\_neg$, which means the segment does not contain the object, we cut all the nodes below and return NULL. If the similarity is between $thre\_perf$ and $thre\_pos$, which means the node definitely contains the object but the segmentation is not perfect yet, we keep on checking its children nodes to refine the segmentation. The final case is that the similarity is between $thre\_pos$ and $thre\_neg$, which means we are not sure whether there is an object in the node, so we just keep on searching its children.

@@

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:} 
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE $m_n$ := mask of $n$
  \STATE $pred\_model$ := predict attributes on image($m_n \cap m_m$)
  \STATE $sim=HI(obj\_model,pred\_model)$
  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$sim < f sim_{root}$}
    \FOR{$i=1$ to $n.childNum$} 
      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
      \STATE ...$sim_{root}$, $f$)
    \ENDFOR
    %\STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prune}
\end{algorithm}

The algorithm begins at the root of the tree and predicts attributes.
This attribute distribution and its associated similarity $sim_{root}$ 
to the object's canonical distribution is taken to be
the standard for the image.  That is, any final segmentation should not have
significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
the subtractive tree depth-first, predicting on each node.  
Any node that doesn't have a significant negative effect on the similarity as 
compared to the standard is removed.  If the
similarity was significantly affected, then we know that the region
must remain.  But it doesn't mean that sub-regions might not be able to be pruned
out, so the procedure is called recursively, checking for smaller regions
that might be able to be pruned.

If the probability was not significantly affected, then the mask is applied
and no recursive call is made.  This is important, because it means
that we can remove large chunks of the image wholesale and bypass predicting
on the node's posterity.

@@

The runtime performance of the algorithm is dominated by the prediction step.
Thus the advantage of pruning large chunks early is highly beneficial to 
the runtime of the algorithm.

\begin{figure}
\centering
\subfigure[]{
\label{fig:fa}
\includegraphics[width=0.22\textwidth]{figures/parking_0.9.eps}
}
\subfigure[]{
\label{fig:fb}
\includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
}
\caption{Result of adjusting the factor $f$ in the subtractive algorithm.
\subref{fig:fa} shows running the algorithm with $f=0.9$ and \subref{fig:fb}
shows running the algorithm with $f=1.0$.  Note that \subref{fig:fb} retains
more of the cars, especially the two closest on the right and left, but also
hsa more false-positive pixels, such as the ceiling region of the parking
garage.}
\label{fig:f}
\end{figure}

@@

In this section, we evaluate our attribute based object detection and segmentation algorithm. We will answer four questions. (1) What is the performance of object detection and segmentation? (2) What is the influences of different parameters? (3) What are the advantages of the two pruning algorithms? (4) Is vertical confidence propogation useful?

@@

We use the Pascal2008 dataset.  The attribute annotations used in \cite{farhadi09}
are freely available and we used them for training the attributes.

\ref{table:aresults} shows some of the results from running the additive algorithm
on all cars in the dataset.  The recall is the rate of correctly detecting
images with cars.  The segmentation precision is calculated with
\[ V(M_{model},M_{pred}) = \frac{|M_{model} \cap M_{pred}|}{|M_{model} \cup M_{pred}|} \]
where $M_{model}$ is the model mask calculated from the bounding boxes
stored with the annotations and $M_{pred}$ is the predicted segmentation
mask.  We of course recognize that the bounding boxes are not a good measure
of segmentation truth, but it's the best we have available.

@@

Figures \ref{fig:good_results} and \ref{fig:bad_results} show the results
of segmentations of various images by both images.  This shows clear linkage
between prominence of the side profile of the car and success of the segmentation.
It appears that the attribute classifiers are more accurate on side profiles
than front and rear shots, although rear shots performed reasonably well when
tail lights were not illuminated.

\begin{table}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
$P$ & $D$ & recall & prec \\ \hline
4, 1 & 227 & 0.4317 & 0.2393 \\ \hline
4, 1.5 & 239 & 0.3849 & 0.2370 \\ \hline
6, 1.5 & 239 & 0.2720 & 0.2501 \\ \hline
\end{tabular}
\caption{Results from the additive algorithm on all car images.  $P$ is
the parameters, $D$ is the number of detections, recall is the detection
recall rate and prec is the segmentation precision on all detected
images.}
\label{table:aresults}
\end{table}

@@

>>>>

Our work focuses on leveraging attributes to produce accurate segmentations.
The idea is to find image regions with attribute distributions very similar
to some canonical distribution for an object.  We define the ``canonical distribution''
to be an attribute distribution representative of that object.  For example, the
canonical distribution for a ``car'' would have some measure of ``shininess'', some
other measure of ``window'' and so forth.  If
regions can be combined together to for larger regions with attribute
distributions matching the object's canonical distribution then one can
declare the combined region an accurate segmentation for that object.

We note that it is possible that one segmented region may contain the object and
nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
simple objects, the true region of the object is distributed among various
segmentations.  This is because all but the most trivial objects have different
sub-regions of different colors, textures, contours, etc.  Thus we must search
for a combination of these sub-regions that make up the object.

\begin{figure}
\centering
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_orig_med.eps}
\label{fig:trucka}
}
\subfigure[]{
\includegraphics[width=0.22\textwidth]{figures/truck_final_med.eps}
\label{fig:truckb}
}
\caption{Segmentation by maximizing attribute similarity to a canonical
attribute distribution for a car.  \subref{fig:trucka} shows
the original image with any ``car'' attributes that were predicted.  $P$ is the probability
that the image contains a car.  \subref{fig:truckb} shows the segmented image after
running our segmentation tree pruning algorithm.  As extraneous regions are pruned
more car attributes are predicted and the probability that the remaining image
contains a car increases.}
\label{fig:truck}
\end{figure}

In general, the testing of all combinations of regions to
find objects is intractable.  We use two approximatory algorithms
operating on a segmentation hierarchy to determine regions belonging
to a given class.
One algorithm is additive and operates by combining regions that are likely
to be part of the object.  The other is subtractive, which first predict attributes on
the entire region and then proceeds by observing the effects of
removing different regions during a top-down traversal of the tree.
The benefit of using these methods are that large regions that
clearly don't contribute to an attribute distribution similar to the
canonical can be pruned from
the tree early in the traversal.  This approach avoids the
combinatoric complexity of a full search and, even more, prunes many
regions from the segmentation tree before they even are searched,
bringing the computational complexity, in practice, to roughly
$O(n)$ where $n$ is the number of leaves in the segmentation tree.
The flowchart of our algorithm is shown in Figure
\ref{fig:flowchart}.

This work is done using attributes as the features, but the segmentation
pruning algorithms are actually feature-type agnostic and could be used
with any image feature given a scoring function applicable to that feature.

While we focus on segmentation of known objects, we anticipate an application
that takes more advantage of attributes: that of segmenting \emph{unknown}
objects from an image that exhibit stable but unrecognized attribute
distributions.  This type of application brings out some of the true power of
attributes, that of assigning semantic meaning to unknown, segmented objects.

@@

%-------------------------------------------------------------------------------
% related work
%-------------------------------------------------------------------------------
\section{Related work}
\label{sec:related_work}
A significant amount of recent work has been done in the area of using
attributes as high-level features for image classification and object
description \cite{farhadi09, lampert09, kumar09}.
Another area of computer vision, that of segmentation,
has seen a resurgence of popularity as methods to incorporate top-down
information into segmentation have been shown to be highly effective
\cite{borenstein04, pantofaru, gu09, russell06, malisiewicz, leibe04, hoiem05, shotton06}.
We propose to leverage research done in both of these areas -- attributes
and top-down/bottom-up segmentation -- to produce a combined approach.

@@

Object classification can give some top-down high-level information
for segmentation. On the other hand, segmentation can provide
image-based coherence information for classification. To deal with
the problem that the bottom-up single segmentation is not accurate,
more and more algorithms are based on multiple segmentations. Gu et
al \cite{gu09} uses the hierarchical segmentation algorithm to
generate multiple segments, and detect different parts of objects in
each segment. The final objects are voted for by the various parts.
We will initially be using the same segmentation algorithm used in
this paper, but without discarding the hierarchy.
Russell et al \cite{russell06} detect the whole object in each of
the multiple segment, by assuming that most objects get segmented
correctly at least once during the multiple segmentation. Our approach
will be far less aggressive in that we will use object classes and
features (attributes in our case) that are known \emph{a priori}.
Pantofaru et
al \cite{pantofaru} use three different segmentation algorithms to
generate the multiple segments. After detecting objects in each
segment, they merge the intersected segments as final results. In
our method, we use common knowledge of distribution of attributes to
merge segments.
Borenstein et al \cite{borenstein04} proposed a method of combining top-down
and bottom-up information to generate a high-quality segmentation.  Their
approach to the top-down is to use exemplar image fragments and match them
to the image and then refining the top-down segmentation using their
segmentation hierarchy.  Our approach doesn't use any confidence boosting based
on the hierarchy like they do, but rather, the hierarchy is used to guide
efficient removal and combination of regions.

%Another interesting work is that of Gould et al \cite{gould08}.  They use
%superpixels for an initial segmentation, build a CRF that includes a
%relative location feature in the energy function and minimizes the CRF
%for a final segmentation.  The relative location feature is determined
%using prior location probability maps.  Our approach is similar to this
%as well, in that we will also incorporate relative location information,
%although ours will use attributes' relative locations rather than object
%classes.  We will also use a CRF for the final segmentation, but will
%use a min-cut solution since our labels are binary.
%Kumar et al \cite{kumar05} incorporate shape structure into the segmentation by
%adding a latent shape parameter to the CRF.  This seems like it would be
%a useful addition to our system but make the scope too large.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/flowchart.eps}
\caption{Flowchart of the proposed algorithm.} \label{fig:flowchart}
\end{figure}

@@

We use a similar algorithm to that used in \cite{farhadi09} to train the attribute models. Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.  We use kmeans to quantize the features. The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively. All quantized features are concatenated to form a 1384 dimensional feature.  These low-level features are generated for training and testing datasets using the entire image.  This is done to avoid introducing any feature artifacts as a result of black space surrounding segmented regions.

For training, we use an SVM classifier with a Gaussian kernel to train
the model for each attribute.

%The precision of all the attributes on the test set is illustrated
%in figure?.

@@

We use the segmentation approach of \cite{arbelaez09}.  This
produces a hierarchical segmentation by first detecting contours
using the \emph{gPb} detector \cite{maire08}.  This contour detector
is advantageous because it uses brightness, color and texture
gradients at multiple scales.  Once the contours are
detected, regions are discovered using a watershed algorithm after
which an Ultrametric Contour Map (UCM) is constructed, which defines
the region hierarchy.  The UCM is stored as a grayscale image with
contours around the segmented regions.  These contours have intensities
representative of the region's location in the hierarchy.  So to find
the first branch in the tree, threshold the UCM image with a value
$t$ where $t = max{I(x,y)}$ where $I(x,y)$ is the intensity at pixel
location $(x,y)$.  The thresholded image can then be flood-filled into
regions.  These regions correspond to the branches on either side of
the root node in the segmentation tree.  The next level of the tree is
found by thresholding the two new regions of the UCM at each, respective,
next highest intensity and so on.
Figure \ref{fig:ucm} shows an example UCM image and figure \ref{fig:tree}
shows the hierarchy generated from that UCM.

After the construction of segmentation tree, we detect all
the attributes in each node, including the intermediate and
leaf nodes. We use the output of SVM as the confidence (not binary),
so each node can be represented by the confidence distribution of
all attributes.  These distributions are stored and later used in
the additive pruning algorithm.  Unfortunately the subtractive algorithm
requires runtime predictions, and thus cannot use this preprocessing
step.

@@

Our objective is to detect objects and segment them out. Using a segmentation tree
we cast the problem into one of selecting nodes that belong 
to the desired object. We estimate the
probability that a node belongs to object based on the attribute
confidence distribution. For each object, we manually determine a
canonical attribute distribution.  We use the
histogram intersection between the desired distribution and the
estimated confidence distribution in each node as the similarity
measure. The histogram intersection is calculated as follows:

\[ HI(H_{model},H_{pred}) = \frac{|H_{model} \cap H_{pred}|}{|H_{model}|}
\] ,

where $H_{model}$ and $H_{pred}$ represent the desired attribute
distribution and predicted distribution.

To select the nodes, we use two different top-down pruning algorithms, 
the ``additive'' algorithm and the ``subtractive'' algorithm. 
Each of these algorithms prunes the region tree until a final segmentation
meeting some criterion of absolute or relative attribute similarity to the canonical is found.
We now discuss each algorithm in detail.

\begin{figure}
\centering
\includegraphics[width=0.30\textwidth]{figures/2008_000052_ucm.bmp.eps}
\caption{A UCM image from which a segmentation tree is derived.}
\label{fig:ucm}
\end{figure}

\begin{figure}
\centering
%\subfigure[]{
%\label{fig:treea}
\includegraphics[width=0.45\textwidth]{figures/tree_additive.eps}
%}
%\subfigure[]{
%\label{fig:treeb}
%\includegraphics[width=0.45\textwidth]{figures/tree_subtractive.eps}
%}
\caption{The segmentation hierarchy used by the additive
and subtractive algorithms.  This tree was generated from the UCM
in figure \ref{fig:ucm}.}
\label{fig:tree}
\end{figure}

@@

This pruning algorithm is based on three observations. (1) At least
one node in the segmentation tree contrains the whole object. (This
is always true since the root node contains the whole image). (2) If
both parent node and child node have high confidence of containing
the object, the segmentation of the child node is more accurate than
that of the parent node. (3) Even if some node has high confidence
of containing the object, its segmentation can still be improved by
removing irrelevant children node. The details of the additive
algorithm is shown in algorithm \ref{alg:add_prune}.

The idea of the algorithm is to find the smallest discriminative
regions, either positive or negative. We combine all the smallest
positive regions while remove all the negative ones to form the
final segmentation. We use three threshold for the similarity
measure, $thre\_perf$, $thre\_pos$ and $thre\_neg$ which represent
perfect segment, positive segment and negative segment,
respectively. If the similarity is above $thre\_perf$, which means
the segmentation is perfect for the object, we cut all the nodes
below and return this segment. If the similarity is below
$thre\_neg$, which means the segment does not contain the object, we
cut all the nodes below and return NULL. If the similarity is
between $thre\_perf$ and $thre\_pos$, which means the node
definitely contains the object but the segmentation is not perfect
yet, we keep on checking its children nodes to refine the
segmentation. The final case is that the similarity is between
$thre\_pos$ and $thre\_neg$, which means we are not sure whether
there is an object in the node, so we just keep on searching its
children.

@@

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:}
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE \textbf{output:}
  \STATE \hspace{3 mm} mask $m_m$
  \STATE
  \STATE $m_n$ := mask of $n$
  \STATE $r = m_{m} \cap \verb+~+ m_{n}$
  \STATE $pred\_model$ := predict attributes on image($r$)
  \STATE $sim=HI(obj\_model,pred\_model)$
  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$sim < f sim_{root}$}
    \FOR{$i=1$ to $n.childNum$}
      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
      \STATE ...$sim_{root}$, $f$)
    \ENDFOR
    %\STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap \verb+~+ m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prune}
\end{algorithm}

The algorithm begins at the root of the tree and predicts attributes.
This attribute distribution and its associated similarity $sim_{root}$
to the object's canonical distribution is taken to be
the standard for the image.  That is, any final segmentation should not have
significantly less similarity $sim$ than $sim_{root}$.  The algorithm traverses
the subtractive tree depth-first.  At each node, attributes are predicted for 
a region $r$.  
$r$ is obtained by taking the intersection of the master mask and the inverted
node mask ($r = m_{m} \cap \verb+~+ m_{n}$).  The intuition is this: the master mask is our current best guess at
the region that contains an object.  By taking the intersection, we effectively
subtract the node's region out.
We can then predict on the new region.  If 
there is no significant negative effect on the similarity as
compared to the standard, then we assume that we can safely prune off the node's
region without removing a part of the object..  If the
similarity was significantly affected, then we assume that the region
contains some part of the object and we allow it to remain.  But that 
doesn't mean that sub-regions might not be able to be pruned
out, so the procedure is called recursively, checking for smaller regions
that might be able to be pruned.

As mentioned, if the similarity score was not significantly affected by
predicting on the master mask with the region removed, then the region is
permanently removed from the master mask
and no recursive call is made.  This is important, because it means
that we can remove large chunks of the image wholesale and bypass predicting
on the node's posterity.
The runtime performance of the algorithm is dominated by the prediction step.
Thus the advantage of pruning large chunks early is highly beneficial to
the runtime of the algorithm.

@@

The subtractive algorithm knows nothing about the number of objects present
in the image.  It attempts to segment any object out into the final region.
This is evident in figure \ref{fig:sub1}.  The mobile homes in the background
have car attributes and thus are included in the final segmentation, even
though they take a far less prominent role in the unsegmented image.  Another
example is figure \ref{fig:truck}, where the two cars visually behind the truck
are segmented alongside the truck.

\begin{figure}
\centering
\subfigure[]{
\label{fig:fa}
\includegraphics[width=0.22\textwidth]{figures/parking_0.9.eps}
}
\subfigure[]{
\label{fig:fb}
\includegraphics[width=0.22\textwidth]{figures/parking_1.0.eps}
} \caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:f}
\end{figure}

\begin{figure}
\centering
\subfigure[]{
\label{fig:sub1a}
\includegraphics[width=0.22\textwidth]{figures/results/2008_000052.jpg.eps}
}
\subfigure[]{
\label{fig:sub1b}
\includegraphics[width=0.22\textwidth]{figures/2008_000052_1.00.jpg.eps}
} \caption{Subtractive segmentation on an image with multiple objects.
An observer may not even notice the trailer homes in the background in
the original image \subref{fig:sub1a},
but the segmentation includes a portion of them in the final segmentation \subref{fig:sub1b}.
Subtractive segmentation attempts to segment all objects present
in the image.}
\label{fig:sub1}
\end{figure}

@@

In this section, we evaluate our attribute based object detection
and segmentation algorithm. We will answer four questions. (1) What
is the performance of object detection and segmentation? (2) What are
the influences of different parameters? (3) What are the advantages
of the two pruning algorithms? (4) Is vertical confidence
propagation useful? (In this draft, we only have partial results, so
not all the questions are considered.)

@@

We use the Pascal2008 dataset. This dataset has a lot of real life
images which are more difficult to classify. The objects are labeled
by bounding boxes not accurate segmentation. For training the
attributes, we use the pascal2008 training set. The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for training too. For testing the classification and
segmentation, we use the pascal2008 validation set. We plan to do
three classes classification and segmentation, including car,
aeroplane and horse. Now we only got the results on car. We will
incorporate the other classes in the final version.

Table \ref{table:aresults} shows some of the results from running
the additive algorithm on all cars in the dataset.  The recall is
the rate of correctly detecting images with cars.  The segmentation
precision is calculated with
\[ V(M_{groundtruth},M_{pred}) = \frac{|M_{groundtruth} \cap M_{pred}|}{|M_{groundtruth} \cup M_{pred}|} \]
where $M_{groundtruth}$ is the groundtruth mask calculated from the
bounding boxes stored with the annotations and $M_{pred}$ is the
predicted segmentation mask.  We of course recognize that the
bounding boxes are not a good measure of segmentation truth, but
it's the best we have available.

@@

Figures \ref{fig:good_results} and \ref{fig:bad_results} show the
results of segmentations of various images by both pruning
algorithms. Figure \ref{fig:good_results} shows some good results,
while Figure \ref{fig:bad_results} shows some bad results. This
shows clear linkage between prominence of the side profile of the
car and success of the segmentation. It appears that the attribute
classifiers are more accurate on side profiles than front and rear
shots, although rear shots performed reasonably well when tail
lights were not illuminated.

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Methods & Precision(\%) & Recall(\%) \\
\hline LowFea  & 55.97 & 70.96 \\
\hline Att1    & 51.89 & 51.89 \\
\hline Random  & 35.19 & 50.00 \\
\hline Add     & 60.82 & 54.06 \\
\hline
\end{tabular}
\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
\label{table:aresults}
\end{table}

@@

Another problem with the attribute based method is that the attributes are not discriminative 
enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
But those attributes can definitely separate the two objects from non-animal objects, such as car. This example demonstrates that 
attributes are helpful for the object classification, but they are not discriminative enough. So one way to deal with this is to use 
both attributes features and low level objects features for object classification. We can train a general attributes models first. 
When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.
